Covariates analysis of MSBB reprocessed RNASeq data

### 2016-05-31 code/Rmd/MSSM_RNASeq_cdr_Reprocessed.Rmd
Minor fix

## Load required libraries
library(CovariateAnalysis) # Get the utilities package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)

@@

tree = hclust(as.dist(t(RESIDUAL.GENE_EXPRESSION)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
tmp = gsub('\\..*','',cols)
WGCNA::plotDendroAndColors(tree, 
                           colors = tmp, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```
```{r get.gene.symbols, cache=TRUE, eval=FALSE}
# Define biomart object
mart <- useMart(biomart = "ensembl", dataset = "hsapiens_gene_ensembl", host = )

>>>>

## Load required libraries
library(CovariateAnalysis) # Get the utilities package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(dplyr)

@@

tree = hclust(as.dist(t(RESIDUAL.GENE_EXPRESSION)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
tmp = gsub('\\..*','',cols)
WGCNA::plotDendroAndColors(tree, 
                           colors = tmp, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```
```{r get.gene.symbols, cache=TRUE, eval=TRUE}
# Define biomart object
mart <- useMart('ENSEMBL_MART_ENSEMBL', dataset = "hsapiens_gene_ensembl", host = 'dec2015.archive.ensembl.org')
